---
title: "Journey Prevention Investigation"
author: "Garrett Jenkins"
date: "2026-06-22"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading

``` {r loading_configuration}

library(dplyr)
library(stringr)
library(purrr)
library(tidyr)
library(psych)
library(lme4)
library(lmerTest)
library(ggplot2)
library(ggeffects)
library(tvem)
library(tidyverse)
library(lubridate)

Daily_Checks <- read.csv("C:/Users/Owner/Downloads/Daily Checkins.csv")

Daily_Checks$DAILY <- 1

colnames(Daily_Checks)[colnames(Daily_Checks) == "CHECKINDATE"] <- "EVENTDATE"

Monthly_Assessments <- read.csv("C:/Users/Owner/Downloads/Monthly Assessments.csv")

Monthly_Assessments$MONTHLY <- 1

colnames(Monthly_Assessments)[colnames(Monthly_Assessments) == "ASSESSMENTDATE"] <- "EVENTDATE"

Platform_Events <- read.csv("C:/Users/Owner/Downloads/Platform Events.csv")

#Comprehensive_DF <- merge(Monthly_Assessments, Platform_Events, by = c('USERID', 'EVENTDATE'), all.x = TRUE)

drop_list <- c("\\[", "\"", " ", "\\]")

pattern <- paste0(drop_list, collapse = "|")

Platform_Events$PLATFORMEVENTS <- gsub(pattern, "", Platform_Events$PLATFORMEVENTS)

Platform_Events <- Platform_Events %>%
  mutate(PLATFORMEVENTS = map_chr(str_split(PLATFORMEVENTS, ","), ~ paste(unique(str_trim(.x)), collapse = ",")))

Platform_Events <- Platform_Events %>%
  separate_longer_delim(PLATFORMEVENTS, delim = ",") %>%
  mutate(PLATFORMEVENTS = trimws(PLATFORMEVENTS), present = 1) %>%
  pivot_wider(
    names_from = PLATFORMEVENTS,
    values_from = present,
    values_fill = 0,
    values_fn = max # Ensures a 1 is kept if a word accidentally repeats in a cell
  )

Comp_DF <- merge(Platform_Events, Daily_Checks, by = c('USERID', 'EVENTDATE'), all.x = TRUE)

Comp_DF <- merge(Comp_DF, Monthly_Assessments, by = c('USERID', 'EVENTDATE'), all.x = TRUE)

Comp_DF <- Comp_DF[,-c(35,36,39)]

Comp_DF$EVENTDATE <- as.Date(Comp_DF$EVENTDATE)

###write.csv(Comp_DF, "C:/Users/Owner/Downloads/TEST.csv", row.names = FALSE)

```

## Exploration

### Checking that all Journey Event Types have actually observed events
### They do

```{r include=FALSE}

#col_indexes <- c(3:30)

#col_sums <- colSums(Comp_DF[, col_indexes])

#col_sums

```

``` {r descriptives_daily_stress}

#table(Comp_DF$STRESSLEVEL)

```


``` {r coding_indicator_variables}

Comp_DF$BAD_DAY_RISK <- ifelse(Comp_DF$FEELINGRATING == 1, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

Comp_DF$STRESS_RISK <- ifelse(Comp_DF$STRESSLEVEL > 5, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

Comp_DF$DEP_ANX_RISK <- ifelse(Comp_DF$FEELINGSFREQUENCY > 3, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

### Bucket into	moderate, elevated, high-risk
###	Review distribution of daily stress scores > 5 to define

### If stress increases over time by any amount then RISK
### How much increase is moderate, elevated, high-risk?

### If depression/anxiety increases from Never/Almost never to >= “Sometimes” then RISK
### How to define moderate/elevated/high-risk here?

Comp_DF_Stress <- Comp_DF %>%
filter(STRESS_RISK == 1) %>%
  group_by(USERID) %>%
  mutate(mean_stresslevel = mean(STRESSLEVEL, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(STRESS_RISK_GROUP = ntile(mean_stresslevel, 3))

Comp_DF_Stress <- Comp_DF_Stress[, c("USERID", "STRESS_RISK_GROUP")] %>%
                  distinct(USERID, .keep_all = TRUE)
  
Comp_DF <- merge(Comp_DF, Comp_DF_Stress, by = 'USERID', all.x = TRUE)

Comp_DF_Dep_Anx <- Comp_DF %>%
filter(DEP_ANX_RISK == 1) %>%
  group_by(USERID) %>%
  mutate(mean_dep_anx = mean(FEELINGSFREQUENCY, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(DEP_ANX_RISK_GROUP = ntile(mean_dep_anx, 3))

Comp_DF_Dep_Anx <- Comp_DF_Dep_Anx[, c("USERID", "DEP_ANX_RISK_GROUP")] %>%
                  distinct(USERID, .keep_all = TRUE)
  
Comp_DF <- merge(Comp_DF, Comp_DF_Dep_Anx, by = 'USERID', all.x = TRUE)


#########   Start Here   ####################

### For bad day risk bucketing, maybe look at frequency of occurrences for individuals
#Comp_DF <- Comp_DF %>%
#filter(BAD_DAY_RISK == 1) %>%
#  group_by(USERID) %>%
#  mutate(mean_stresslevel = mean(STRESSLEVEL, na.rm = TRUE),
#         STRESS_RISK_GROUP = ntile(mean_stresslevel, 3)) %>%
#  ungroup()







Comp_DF$CHALLENGING_DAYS_RISK <- ifelse(Comp_DF$DAYSEMOTIONALLYCHALLENGING > 0, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

Comp_DF$MANAGE_STRESS_RISK <- ifelse(Comp_DF$MANAGESTRESSLEVEL <= 3, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

#Comp_DF$RISK <- ifelse(Comp_DF$FEELINGRATING == 1 | Comp_DF$STRESSLEVEL > 5 | Comp_DF$DAYSEMOTIONALLYCHALLENGING > 0 | Comp_DF$MANAGESTRESSLEVEL <= 3, 1, 0)

Comp_DF <- Comp_DF %>%
  group_by(USERID) %>%
  mutate(
    BASELINE_STRESS = first(STRESSLEVEL[EVENTDATE == min(EVENTDATE)]),
    BASELINE_COPING = first(MANAGESTRESSLEVEL[EVENTDATE == min(EVENTDATE)]),
    BASELINE_CHALLENGING = first(DAYSEMOTIONALLYCHALLENGING[EVENTDATE == min(EVENTDATE)]),
    BASELINE_DEP_ANX = first(FEELINGSFREQUENCY[EVENTDATE == min(EVENTDATE)]),
    STRESS_INCREASED = as.integer(STRESSLEVEL > BASELINE_STRESS & EVENTDATE != min(EVENTDATE)),
    COPING_DECREASED = as.integer(MANAGESTRESSLEVEL < BASELINE_COPING & EVENTDATE != min(EVENTDATE)),
    DAYS_CHALLENGING_INCREASED = as.integer(DAYSEMOTIONALLYCHALLENGING > BASELINE_CHALLENGING & EVENTDATE != min(EVENTDATE)),
    DEP_ANX_INCREASED = as.integer(FEELINGSFREQUENCY > BASELINE_DEP_ANX & EVENTDATE != min(EVENTDATE)),
    PERIOD_RISK = as.integer(
      (BAD_DAY_RISK == 1) |
        (STRESS_RISK == 1) |
        (DEP_ANX_RISK == 1) |
        (CHALLENGING_DAYS_RISK == 1) |
        (MANAGE_STRESS_RISK == 1) |
        (STRESS_INCREASED == 1) |
        (COPING_DECREASED == 1) |
        (DAYS_CHALLENGING_INCREASED == 1) |
        (DEP_ANX_INCREASED == 1)
    ),
    ANY_RISK = as.integer(
      any(BAD_DAY_RISK == 1,
          STRESS_RISK == 1,
          DEP_ANX_RISK == 1,
          CHALLENGING_DAYS_RISK == 1,
          MANAGE_STRESS_RISK == 1,
          STRESS_INCREASED == 1,
          COPING_DECREASED == 1,
          DAYS_CHALLENGING_INCREASED == 1,
          DEP_ANX_INCREASED == 1,
          na.rm = TRUE))
  ) %>%
  ungroup() %>%
  arrange(USERID, EVENTDATE)

### How to define moderate/elevated/high-risk for those who indicate a drop in ability to cope (COPING_DECREASED)

Comp_DF$ANY_RISK <- ifelse(is.na(Comp_DF$ANY_RISK), 0, Comp_DF$ANY_RISK)

Comp_DF$PERIOD_RISK <- ifelse(is.na(Comp_DF$PERIOD_RISK), 0, Comp_DF$PERIOD_RISK)

second_cols <- names(Comp_DF)[3:30] 

### Event Totals Between Monthly Assessment Types

for (col in second_cols) {
  sum_col <- paste0(col, "_MONTHLY_SUM")
  
  Comp_DF <- Comp_DF %>%
    group_by(USERID) %>%
    arrange(USERID, EVENTDATE) %>%
    mutate(PERIOD = cumsum(!is.na(MONTHLY))) %>%
    group_by(USERID, PERIOD) %>%
    mutate(!!sum_col := sum(.data[[col]], na.rm = TRUE)) %>%
    ungroup() %>%
    select(-PERIOD)
}

### Event Totals Between Daily Check-in Assessment Types

for (col in second_cols) {
  sum_col <- paste0(col, "_DAILY_SUM")
  
  Comp_DF <- Comp_DF %>%
    group_by(USERID) %>%
    arrange(USERID, EVENTDATE) %>%
    mutate(PERIOD = cumsum(!is.na(DAILY))) %>%
    group_by(USERID, PERIOD) %>%
    mutate(!!sum_col := sum(.data[[col]], na.rm = TRUE)) %>%
    ungroup() %>%
    select(-PERIOD)
}

Comp_DF <- Comp_DF %>%
  mutate(across(
      ends_with("_SUM"),
    ~ lag(.x)
  ))

Comp_DF$Comp_JOURNEY_USE_M <- rowSums(Comp_DF[grep("MONTHLY_SUM", names(Comp_DF))])

Comp_DF$Comp_JOURNEY_USE_D <- rowSums(Comp_DF[grep("DAILY_SUM", names(Comp_DF))])

```

## Subsetting to Monthly and Daily Trend Analysis File

``` {r Subsetting_analytic_files}

### Creating data file for those who start as Not-at-Risk and later transition to At-Risk

Transitioned_Data <- Comp_DF[, -c(3:30,56:111)]

Transitioned_Users <- Transitioned_Data %>%
  arrange(USERID, EVENTDATE) %>%
  group_by(USERID) %>%
  mutate(ever_zero_so_far = cummax(PERIOD_RISK == 0)) %>%
  filter(PERIOD_RISK == 1 & lag(ever_zero_so_far, default = FALSE)) %>%
  ungroup() %>%
  distinct(USERID) %>%
  pull(USERID)

# Step 2: Subset to keep ALL rows for those USERIDs
Transitioned_Data <- Transitioned_Data %>%
  filter(USERID %in% Transitioned_Users)

Transitioned_Data <- Transitioned_Data %>%
  arrange(USERID, EVENTDATE) %>%
  group_by(USERID) %>%
  mutate(
    PERIOD = cumsum(!is.na(MONTHLY))  # increments every time a MONTHLY checkpoint is hit
  ) %>%
  ungroup()

period_use_sums <- Transitioned_Data %>%
  group_by(USERID, PERIOD) %>%
  summarise(Comp_JOURNEY_USE_SUM = sum(Comp_JOURNEY_USE_D, na.rm = TRUE), .groups = "drop")

Monthly_Risk_Transition <- Transitioned_Data %>%
  left_join(period_use_sums, by = c("USERID", "PERIOD"))

Monthly_DF <- Comp_DF[which(Comp_DF$MONTHLY == 1), -c(3:30)]  ### Update columns here if needed to remove appropriate vars

Monthly_DF$TOTAL_JOURNEY_USE_M <- rowSums(Monthly_DF[grep("MONTHLY_SUM", names(Monthly_DF))])

Monthly_DF_Risk <- Monthly_DF[which(Monthly_DF$ANY_RISK == 1),]

Monthly_DF_Risk_R <- Monthly_DF_Risk[, -grep("_SUM", names(Monthly_DF_Risk))]

obs_per_person <- table(Monthly_DF_Risk_R$USERID)

Monthly_DF_Risk_Modeling <- Monthly_DF_Risk_R[Monthly_DF_Risk_R$USERID %in% names(obs_per_person[obs_per_person >= 3]), ]

Daily_DF <- Comp_DF[which(Comp_DF$DAILY == 1), -c(3:30)]  ### Update columns here if needed to remove appropriate vars

Daily_DF$TOTAL_JOURNEY_USE_D <- rowSums(Daily_DF[grep("DAILY_SUM", names(Daily_DF))])

Daily_DF_Risk <- Daily_DF[which(Daily_DF$ANY_RISK == 1),]

Daily_DF_Risk_R <- Daily_DF_Risk[, -grep("_SUM", names(Daily_DF_Risk))]

obs_per_person <- table(Daily_DF_Risk_R$USERID)

Daily_DF_Risk_Modeling <- Daily_DF_Risk_R[Daily_DF_Risk_R$USERID %in% names(obs_per_person[obs_per_person >= 3]), ]

Monthly_Dep_Anx_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 1),]

Monthly_Dep_Anx_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 2),]

Monthly_Dep_Anx_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 3),]

Monthly_Stress_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 1),]

Monthly_Stress_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 2),]

Monthly_Stress_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 3),]

```

``` {r sample_size_frequencies}


### Based on the information Journey has provided, there appear to be approximately 6,700 participants with repeated assessment ### data and roughly 10,600 participants with repeated daily check-ins.


Comp_DF %>%
  count(USERID) %>%
  #filter(n > 2) %>%
  summarise(distinct_users = n())

Daily_Checks %>%
  group_by(USERID) %>%
  summarise(
    sum_daily   = sum(DAILY, na.rm = TRUE)
  ) %>%
  filter(sum_daily > 1) %>%
  summarise(distinct_users = n())


Monthly_Assessments %>%
  group_by(USERID) %>%
  summarise(
    sum_monthly = sum(MONTHLY, na.rm = TRUE)
  ) %>%
  filter(sum_monthly > 1) %>%
  summarise(distinct_users = n())


  Comp_DF %>%
  group_by(USERID) %>%
  summarise(
    sum_daily   = sum(DAILY, na.rm = TRUE),
    sum_monthly = sum(MONTHLY, na.rm = TRUE)
  ) %>%
  filter(sum_daily > 1 & sum_monthly > 1) %>%
  summarise(distinct_users = n())


```

``` {r monthly_out_pred_correlations}

Outcomes <- c("STRESSLEVEL", "MANAGEFEELINGSLEVEL", "FEELINGSFREQUENCY", "DAYSEMOTIONALLYCHALLENGING", "MANAGESTRESSLEVEL")

Pred_Out_M <- Monthly_DF[, which(grepl("MONTHLY_SUM", names(Monthly_DF)) | names(Monthly_DF) %in% Outcomes)]

Cors_list <- NULL

for (i in Outcomes) {

ctest_M <- corr.test(Pred_Out_M)
r_value_M <- round(ctest_M$r[, i], 4)
p_value_M <- round(ctest_M$p[, i], 4)
n_value_M <- ctest_M$n[, i]

Monthly_Cors <- data.frame(Correlation = r_value_M, P_Value = p_value_M, N = n_value_M, Outcome = i)

Monthly_Cors$Predictor <- sub(".*\\.", "", rownames(Monthly_Cors))

  Cors_list[[i]] <- Monthly_Cors
  
}

Monthly_Cors_DF <- do.call(rbind, Cors_list)

rownames(Monthly_Cors_DF) <- NULL

```

``` {r daily_out_pred_correlations}

Pred_Out_D <- Daily_DF[, which(grepl("DAILY_SUM", names(Monthly_DF)) | names(Monthly_DF) %in% Outcomes)]

for (i in Outcomes){

ctest_D <- corr.test(Pred_Out_D)
r_value_D <- round(ctest_D$r[, i], 4)
p_value_D <- round(ctest_D$p[, i], 4)
n_value_D <- ctest_D$n[, i]

Daily_Cors <- data.frame(Correlation = r_value_D, P_Value = p_value_D, N = n_value_D, Outcome = i)

Daily_Cors$Predictor <- sub(".*\\.", "", rownames(Daily_Cors))

  Cors_list[[i]] <- Daily_Cors
  
}

Daily_Cors_DF <- do.call(rbind, Cors_list)

rownames(Daily_Cors_DF) <- NULL

```

``` {r monthly_analyses}

###Risk Signals → Journey Use → Improvement
###Risk Signals → Journey Use → No Improvement
###Risk Signals → Limited/No Journey Use → Worsening Risk

# Standardize (z-score) TOTAL_JOURNEY_USE_M

Monthly_DF_Risk_Modeling <- Monthly_DF_Risk_Modeling %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_DF_Risk_Modeling$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_DF_Risk_Modeling$TOTAL_JOURNEY_USE_M)[,1]





















# Random intercept model: allows each person to have their own baseline stress level

model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

```

``` {r daily_analyses}

###Risk Signals → Journey Use → Improvement
###Risk Signals → Journey Use → No Improvement
###Risk Signals → Limited/No Journey Use → Worsening Risk



# Install and load the tvem and tidyverse packages

# Example formula where the effect of 'predictor1' varies over 'time'
# grouped by 'subject_id'
tvem_model_D <- tvem(
  formula = FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z,
  data = Daily_DF_Risk_Modeling,
  id = USERID,
  time = DATE_NUMERIC,
  family = gaussian() # Use binomial() for binary outcomes
)

# View the summary of the varying coefficients
summary(tvem_model_D)

# Adjust index/name based on what str() shows you
coef_df_D <- tvem_model_D$grid_fitted_coefficients$TOTAL_JOURNEY_USE_D_z

coef_df_D$time <- tvem_model_D$time_grid

library(ggplot2)

ggplot(coef_df_D, aes(x = time)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "steelblue", alpha = 0.2) +
  geom_line(aes(y = estimate), color = "steelblue", linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Time-Varying Effect of Total Use on Stress Level",
    x = "Time (days since first observation)",
    y = "Estimated Effect of Total Daily Journey Use on STRESSLEVEL"
  ) +
  theme_minimal(base_size = 13)












# Standardize (z-score) TOTAL_JOURNEY_USE_M

Daily_DF_Risk_Modeling$TOTAL_JOURNEY_USE_D_z <- scale(Daily_DF_Risk_Modeling$TOTAL_JOURNEY_USE_D)[,1]

Daily_DF_Risk_Modeling <- Daily_DF_Risk_Modeling %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z + (1 | USERID), data = Daily_DF_Risk_Modeling)

summary(model1)

model2 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z + (1 + TOTAL_JOURNEY_USE_D_z | USERID), data = Daily_DF_Risk_Modeling)

summary(model2)

model3 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z * DATE_NUMERIC + (1 | USERID), data = Daily_DF_Risk_Modeling)

summary(model3)

model4 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_D_z | USERID), data = Daily_DF_Risk_Modeling)

summary(model4)

```





``` {r daily_model_plots}

predictions <- ggpredict(model3, terms = "TOTAL_JOURNEY_USE_D_z")

# 3. Plot automatically using ggplot2 logic under the hood
plot(predictions)

# Alternatively, customize it further with standard ggplot2 layers
ggplot(predictions, aes(x = x, y = predicted)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "blue") +
  labs(x = "Days", y = "Predicted Reaction Time", title = "Model Fixed Effects")









```


``` {r tvem_monthly_test}

tvem_model_M <- tvem(
  formula = STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z,
  data = Monthly_Dep_Anx_GRP_1,
  id = USERID,
  time = DATE_NUMERIC,
  family = gaussian() # Use binomial() for binary outcomes
)

# Adjust index/name based on what str() shows you
coef_df_M <- tvem_model_M$grid_fitted_coefficients$TOTAL_JOURNEY_USE_M_z

coef_df_M$time <- tvem_model_M$time_grid

ggplot(coef_df_M, aes(x = time)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "steelblue", alpha = 0.2) +
  geom_line(aes(y = estimate), color = "steelblue", linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Time-Varying Effect of Total Use on Stress Level",
    x = "Time (days since first observation)",
    y = "Estimated Effect of Total Daily Journey Use on STRESSLEVEL"
  ) +
  theme_minimal(base_size = 13)




```


























``` {r monthly_analyses}

###Risk Signals → Journey Use → Improvement
###Risk Signals → Journey Use → No Improvement
###Risk Signals → Limited/No Journey Use → Worsening Risk

# Standardize (z-score) TOTAL_JOURNEY_USE_M


Monthly_Dep_Anx_GRP_1 <- Monthly_Dep_Anx_GRP_1 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_1$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_1$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)






Monthly_Dep_Anx_GRP_2 <- Monthly_Dep_Anx_GRP_2 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_2$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_2$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)












Monthly_Dep_Anx_GRP_3 <- Monthly_Dep_Anx_GRP_3 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)
















Monthly_Stress_GRP_1 <- Monthly_Stress_GRP_1 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Stress_GRP_1$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Stress_GRP_1$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)






Monthly_Stress_GRP_2 <- Monthly_Stress_GRP_2 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Stress_GRP_2$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Stress_GRP_2$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)












Monthly_Stress_GRP_3 <- Monthly_Stress_GRP_3 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Stress_GRP_3$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Stress_GRP_3$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

```

Monthly_Dep_Anx_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 1),]

Monthly_Dep_Anx_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 2),]

Monthly_Dep_Anx_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 3),]

Monthly_Stress_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 1),]

Monthly_Stress_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 2),]

Monthly_Stress_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 3),]






Monthly_Dep_Anx_GRP_3 <- Monthly_Dep_Anx_GRP_3 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

```{r sandbox}

write.csv(abc, "C:/Users/Owner/Downloads/test.csv", row.names = F)

table(Daily_DF$ANY_RISK)

table(Monthly_DF$ANY_RISK)

Monthly_DF$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_DF$TOTAL_JOURNEY_USE_M)[,1]


Monthly_DF <- Monthly_DF %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_DF$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_DF$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + ANY_RISK + (1 | USERID), data = Monthly_DF)

summary(model1)


testdf <- testdf[, -c(27:82)]

model1 <- lmer(TOTAL_JOURNEY_USE_M_z ~ ANY_RISK + (1 | USERID), data = testdf)

summary(model1)




Monthly_Risk_Transition_TEST <- Monthly_Risk_Transition %>%
  arrange(USERID, PERIOD) %>%
  group_by(USERID) %>%
  mutate(
    risk_onset_period = ifelse(any(PERIOD_RISK == 1), PERIOD[which(PERIOD_RISK == 1)[1]], NA),
    phase = case_when(
      is.na(risk_onset_period) ~ NA_character_,
      PERIOD < risk_onset_period ~ "before",
      PERIOD >= risk_onset_period ~ "after"
    )
  ) %>%
  ungroup()

Monthly_Risk_Transition_TEST$Comp_JOURNEY_USE_SUM_z <- scale(Monthly_Risk_Transition_TEST$Comp_JOURNEY_USE_SUM)[,1]



testmodel <- lmer(
  STRESSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 1)
)

summary(testmodel)

testmodel <- lmer(
  MANAGESTRESSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 1)
)

summary(testmodel)

testmodel <- lmer(
  MANAGEFEELINGSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 1)
)

summary(testmodel)


testmodel <- lmer(
  FEELINGSFREQUENCY ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 1)
)

summary(testmodel)


testmodel <- lmer(
  DAYSEMOTIONALLYCHALLENGING ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 1)
)

summary(testmodel)




testmodel <- lmer(
  STRESSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 2)
)

summary(testmodel)

testmodel <- lmer(
  MANAGESTRESSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 2)
)

summary(testmodel)

testmodel <- lmer(
  MANAGEFEELINGSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 2)
)

summary(testmodel)


testmodel <- lmer(
  FEELINGSFREQUENCY ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 2)
)

summary(testmodel)


testmodel <- lmer(
  DAYSEMOTIONALLYCHALLENGING ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 2)
)

summary(testmodel)



testmodel <- lmer(
  STRESSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 3)
)

summary(testmodel)

testmodel <- lmer(
  MANAGESTRESSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 3)
)

summary(testmodel)

testmodel <- lmer(
  MANAGEFEELINGSLEVEL ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 3)
)

summary(testmodel)


testmodel <- lmer(
  FEELINGSFREQUENCY ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 3)
)

summary(testmodel)


testmodel <- lmer(
  DAYSEMOTIONALLYCHALLENGING ~ Comp_JOURNEY_USE_SUM_z * phase + (1 | USERID),
  data = Monthly_Risk_Transition_TEST %>% filter(!is.na(phase)),
  subset = (DEP_ANX_RISK_GROUP == 3)
)

summary(testmodel)





















abc <- Monthly_Risk_Transition

# Make sure EVENTDATE is an actual Date object
abc$EVENTDATE <- as.Date(abc$EVENTDATE, format = "%Y-%m-%d")

# ---- 2. Build START_RISK and END_RISK ------------------------------------
abc <- abc %>%
  group_by(USERID) %>%
  mutate(
    # earliest EVENTDATE among rows where PERIOD_RISK == 1 (NA-safe)
    .start_date = suppressWarnings(
      min(EVENTDATE[!is.na(PERIOD_RISK) & PERIOD_RISK == 1], na.rm = TRUE)
    ),
    # if a USERID has no PERIOD_RISK == 1 rows at all, min() on an empty
    # vector returns Inf -> convert that to NA so comparisons behave
    .start_date = as.Date(ifelse(is.infinite(.start_date), NA, .start_date),
                           origin = "1970-01-01"),

    START_RISK = as.integer(
      !is.na(PERIOD_RISK) & PERIOD_RISK == 1 &
        !is.na(.start_date) & EVENTDATE == .start_date
    ),

    # Is this row within the 5-7 month (inclusive) follow-up window?
    .in_window = !is.na(.start_date) &
      EVENTDATE >= (.start_date %m+% months(5)) &
      EVENTDATE <= (.start_date %m+% months(7)),

    # --- "1" case: earliest EVENTDATE in-window where PERIOD_RISK == 1
    #     AND MONTHLY == 1 ---
    .end1_date = suppressWarnings(
      min(EVENTDATE[.in_window & !is.na(PERIOD_RISK) & PERIOD_RISK == 1 &
                      !is.na(MONTHLY) & MONTHLY == 1],
          na.rm = TRUE)
    ),
    .end1_date = as.Date(ifelse(is.infinite(.end1_date), NA, .end1_date),
                          origin = "1970-01-01")
  ) %>%
  ungroup()

# --- "0" case, part A: flag which (USERID, PERIOD) groups are "clean"
#     -- i.e. every row sharing that PERIOD value has PERIOD_RISK == 0.
#     ASSUMPTION: this is checked only among each USERID's IN-WINDOW rows
#     (the 5-7 month follow-up window), not that PERIOD's entire history
#     in the dataset. Requiring the whole historical PERIOD to be 100%
#     risk-free turned out to be far too strict for this data (almost no
#     PERIOD ever qualifies, since most periods begin with the very risk
#     event that starts them) and produced almost no END_RISK == 0 rows
#     at all. If you actually intended the whole-history version, swap
#     the .filter(.in_window) below to run on the full abc instead. ---
period_clean <- abc %>%
  filter(.in_window) %>%
  group_by(USERID, PERIOD) %>%
  summarise(.period_all_zero = all(!is.na(PERIOD_RISK) & PERIOD_RISK == 0),
            .groups = "drop")

abc <- abc %>%
  left_join(period_clean, by = c("USERID", "PERIOD"))

# --- "0" case, part B: among a USERID's in-window rows that belong to a
#     "clean" PERIOD, find the MAXIMUM such PERIOD value ---
max_clean_period <- abc %>%
  filter(.in_window, .period_all_zero) %>%
  group_by(USERID) %>%
  summarise(.max_period0 = max(PERIOD), .groups = "drop")

abc <- abc %>%
  left_join(max_clean_period, by = "USERID") %>%
  group_by(USERID) %>%
  mutate(
    # --- "0" case, part C: earliest in-window EVENTDATE within that max
    #     clean PERIOD, restricted to rows where MONTHLY == 1 ---
    .end0_date = suppressWarnings(
      min(EVENTDATE[.in_window & !is.na(.max_period0) & PERIOD == .max_period0 &
                      !is.na(MONTHLY) & MONTHLY == 1],
          na.rm = TRUE)
    ),
    .end0_date = as.Date(ifelse(is.infinite(.end0_date), NA, .end0_date),
                          origin = "1970-01-01"),

    # --- If a USERID has BOTH a "1" candidate and a "0" candidate, keep
    #     only whichever EVENTDATE is closer to exactly 6 months after
    #     the START_RISK date; the other candidate is dropped (becomes NA
    #     for that USERID). Ties are broken in favor of the "1" case. ---
    .six_month_mark = .start_date %m+% months(6),
    .dist1 = as.numeric(abs(.end1_date - .six_month_mark)),
    .dist0 = as.numeric(abs(.end0_date - .six_month_mark)),
    .keep1 = !is.na(.end1_date) & (is.na(.end0_date) | .dist1 <= .dist0),
    .keep0 = !is.na(.end0_date) & (is.na(.end1_date) | .dist0 <  .dist1),

    END_RISK = case_when(
      .keep1 & PERIOD_RISK == 1 & !is.na(MONTHLY) & MONTHLY == 1 &
        EVENTDATE == .end1_date ~ 1L,
      .keep0 & PERIOD_RISK == 0 & !is.na(MONTHLY) & MONTHLY == 1 &
        EVENTDATE == .end0_date ~ 0L,
      TRUE ~ NA_integer_
    )
  ) %>%
  ungroup() %>%
  select(-.start_date, -.in_window, -.end1_date, -.period_all_zero,
         -.max_period0, -.end0_date, -.six_month_mark, -.dist1, -.dist0,
         -.keep1, -.keep0)

abc_risk_subset <- abc %>%
  group_by(USERID) %>%
  filter(any(START_RISK == 1, na.rm = TRUE) & any(!is.na(END_RISK), na.rm = TRUE)) %>%
  ungroup()

abc_risk_subset <- abc_risk_subset %>%
  arrange(USERID, PERIOD, EVENTDATE) %>%
  group_by(USERID, PERIOD) %>%
  slice(1) %>%
  ungroup()

abc_risk_subset <- abc_risk_subset[which(abc_risk_subset$START_RISK == 1 | !is.na(abc_risk_subset$END_RISK)),]

abc_risk_subset <- abc_risk_subset %>%
  distinct(USERID, EVENTDATE, .keep_all = TRUE)

Monthly_DF_Outcome_Join <- Monthly_DF[,c("USERID", "EVENTDATE", "TOTAL_JOURNEY_USE_M")]

six_month_risk_outcomes <- abc_risk_subset

six_month_risk_outcomes$EVENTDATE_COPY <- six_month_risk_outcomes$EVENTDATE

six_month_risk_outcomes <- six_month_risk_outcomes[, c("USERID", "EVENTDATE", "EVENTDATE_COPY")]

six_month_risk_outcomes <- merge(six_month_risk_outcomes, Monthly_DF_Outcome_Join, by = c("USERID", "EVENTDATE"), all = TRUE)


six_month_risk_outcomes$EVENTDATE      <- as.Date(six_month_risk_outcomes$EVENTDATE,      format = "%Y-%m-%d")
six_month_risk_outcomes$EVENTDATE_COPY <- as.Date(six_month_risk_outcomes$EVENTDATE_COPY, format = "%Y-%m-%d")

# ---- 2. Build SUM_JOURNEY_USE_M -------------------------------------------
six_month_risk_outcomes <- six_month_risk_outcomes %>%
  arrange(USERID, EVENTDATE) %>%   # make sure rows are in date order within USERID
  group_by(USERID) %>%
  mutate(
    .rn = row_number(),

    # position (row number within the USERID group) of the FIRST row
    # where EVENTDATE_COPY is populated
    .first_pop = suppressWarnings(min(.rn[!is.na(EVENTDATE_COPY)])),
    .first_pop = ifelse(is.infinite(.first_pop), NA_integer_, .first_pop),

    # position of the SECOND row where EVENTDATE_COPY is populated
    # (NA if there is no second populated row for this USERID)
    .second_pop = {
      pop_positions <- sort(.rn[!is.na(EVENTDATE_COPY)])
      if (length(pop_positions) >= 2) pop_positions[2] else NA_integer_
    },

    # last row to include in the sum: the row right before the second
    # populated row, or the last row of the USERID's data if there is
    # no second populated row
    .end_row = ifelse(!is.na(.second_pop), .second_pop - 1L, max(.rn)),

    SUM_JOURNEY_USE_M = ifelse(
      !is.na(.first_pop) & .rn == .first_pop,
      sum(TOTAL_JOURNEY_USE_M[.rn >= .first_pop & .rn <= .end_row],
          na.rm = TRUE),
      NA_real_
    )
  ) %>%
  ungroup() %>%
  select(-.rn, -.first_pop, -.second_pop, -.end_row)

```
