---
title: "Journey Prevention Investigation"
author: "Garrett Jenkins"
date: "2026-06-22"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading

``` {r loading_configuration}

library(dplyr)
library(stringr)
library(purrr)
library(tidyr)
library(psych)
library(lme4)
library(lmerTest)
library(ggplot2)
library(ggeffects)
library(tvem)
library(tidyverse)

Daily_Checks <- read.csv("C:/Users/Owner/Downloads/Daily Checkins.csv")

Daily_Checks$DAILY <- 1

colnames(Daily_Checks)[colnames(Daily_Checks) == "CHECKINDATE"] <- "EVENTDATE"

Monthly_Assessments <- read.csv("C:/Users/Owner/Downloads/Monthly Assessments.csv")

Monthly_Assessments$MONTHLY <- 1

colnames(Monthly_Assessments)[colnames(Monthly_Assessments) == "ASSESSMENTDATE"] <- "EVENTDATE"

Platform_Events <- read.csv("C:/Users/Owner/Downloads/Platform Events.csv")

#Comprehensive_DF <- merge(Monthly_Assessments, Platform_Events, by = c('USERID', 'EVENTDATE'), all.x = TRUE)

drop_list <- c("\\[", "\"", " ", "\\]")

pattern <- paste0(drop_list, collapse = "|")

Platform_Events$PLATFORMEVENTS <- gsub(pattern, "", Platform_Events$PLATFORMEVENTS)

Platform_Events <- Platform_Events %>%
  mutate(PLATFORMEVENTS = map_chr(str_split(PLATFORMEVENTS, ","), ~ paste(unique(str_trim(.x)), collapse = ",")))

Platform_Events <- Platform_Events %>%
  separate_longer_delim(PLATFORMEVENTS, delim = ",") %>%
  mutate(PLATFORMEVENTS = trimws(PLATFORMEVENTS), present = 1) %>%
  pivot_wider(
    names_from = PLATFORMEVENTS,
    values_from = present,
    values_fill = 0,
    values_fn = max # Ensures a 1 is kept if a word accidentally repeats in a cell
  )

Comp_DF <- merge(Platform_Events, Daily_Checks, by = c('USERID', 'EVENTDATE'), all.x = TRUE)

Comp_DF <- merge(Comp_DF, Monthly_Assessments, by = c('USERID', 'EVENTDATE'), all.x = TRUE)

Comp_DF <- Comp_DF[,-c(35,36,39)]

Comp_DF$EVENTDATE <- as.Date(Comp_DF$EVENTDATE)

###write.csv(Comp_DF, "C:/Users/Owner/Downloads/TEST.csv", row.names = FALSE)

```

## Exploration

### Checking that all Journey Event Types have actually observed events
### They do

```{r include=FALSE}

col_indexes <- c(3:30)

col_sums <- colSums(Comp_DF[, col_indexes])

col_sums

```

``` {r descriptives_daily_stress}

table(Comp_DF$STRESSLEVEL)

```


``` {r coding_indicator_variables}

Comp_DF$BAD_DAY_RISK <- ifelse(Comp_DF$FEELINGRATING == 1, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

Comp_DF$STRESS_RISK <- ifelse(Comp_DF$STRESSLEVEL > 5, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

Comp_DF$DEP_ANX_RISK <- ifelse(Comp_DF$FEELINGSFREQUENCY > 3, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

### Bucket into	moderate, elevated, high-risk
###	Review distribution of daily stress scores > 5 to define

### If stress increases over time by any amount then RISK
### How much increase is moderate, elevated, high-risk?

### If depression/anxiety increases from Never/Almost never to >= “Sometimes” then RISK
### How to define moderate/elevated/high-risk here?

Comp_DF_Stress <- Comp_DF %>%
filter(STRESS_RISK == 1) %>%
  group_by(USERID) %>%
  mutate(mean_stresslevel = mean(STRESSLEVEL, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(STRESS_RISK_GROUP = ntile(mean_stresslevel, 3))

Comp_DF_Stress <- Comp_DF_Stress[, c("USERID", "STRESS_RISK_GROUP")] %>%
                  distinct(USERID, .keep_all = TRUE)
  
Comp_DF <- merge(Comp_DF, Comp_DF_Stress, by = 'USERID', all.x = TRUE)

Comp_DF_Dep_Anx <- Comp_DF %>%
filter(DEP_ANX_RISK == 1) %>%
  group_by(USERID) %>%
  mutate(mean_dep_anx = mean(FEELINGSFREQUENCY, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(DEP_ANX_RISK_GROUP = ntile(mean_dep_anx, 3))

Comp_DF_Dep_Anx <- Comp_DF_Dep_Anx[, c("USERID", "DEP_ANX_RISK_GROUP")] %>%
                  distinct(USERID, .keep_all = TRUE)
  
Comp_DF <- merge(Comp_DF, Comp_DF_Dep_Anx, by = 'USERID', all.x = TRUE)


#########   Start Here   ####################

### For bad day risk bucketing, maybe look at frequency of occurrences for individuals
#Comp_DF <- Comp_DF %>%
#filter(BAD_DAY_RISK == 1) %>%
#  group_by(USERID) %>%
#  mutate(mean_stresslevel = mean(STRESSLEVEL, na.rm = TRUE),
#         STRESS_RISK_GROUP = ntile(mean_stresslevel, 3)) %>%
#  ungroup()





















Comp_DF$CHALLENGING_DAYS_RISK <- ifelse(Comp_DF$DAYSEMOTIONALLYCHALLENGING > 0, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

Comp_DF$MANAGE_STRESS_RISK <- ifelse(Comp_DF$MANAGESTRESSLEVEL <= 3, 1, 0)

#Comp_DF$BAD_DAY_RISK <- ifelse(is.na(Comp_DF$BAD_DAY_RISK), 0, Comp_DF$BAD_DAY_RISK)

#Comp_DF$RISK <- ifelse(Comp_DF$FEELINGRATING == 1 | Comp_DF$STRESSLEVEL > 5 | Comp_DF$DAYSEMOTIONALLYCHALLENGING > 0 | Comp_DF$MANAGESTRESSLEVEL <= 3, 1, 0)

Comp_DF <- Comp_DF %>%
  group_by(USERID) %>%
  mutate(
    BASELINE_STRESS = first(STRESSLEVEL[EVENTDATE == min(EVENTDATE)]),
    BASELINE_COPING = first(MANAGESTRESSLEVEL[EVENTDATE == min(EVENTDATE)]),
    BASELINE_CHALLENGING = first(DAYSEMOTIONALLYCHALLENGING[EVENTDATE == min(EVENTDATE)]),
    BASELINE_DEP_ANX = first(FEELINGSFREQUENCY[EVENTDATE == min(EVENTDATE)]),
    STRESS_INCREASED = as.integer(STRESSLEVEL > BASELINE_STRESS & EVENTDATE != min(EVENTDATE)),
    COPING_DECREASED = as.integer(MANAGESTRESSLEVEL < BASELINE_COPING & EVENTDATE != min(EVENTDATE)),
    DAYS_CHALLENGING_INCREASED = as.integer(DAYSEMOTIONALLYCHALLENGING > BASELINE_CHALLENGING & EVENTDATE != min(EVENTDATE)),
    DEP_ANX_INCREASED = as.integer(FEELINGSFREQUENCY > BASELINE_DEP_ANX & EVENTDATE != min(EVENTDATE)),
    PERIOD_RISK = as.integer(
      (BAD_DAY_RISK == 1) |
        (STRESS_RISK == 1) |
        (DEP_ANX_RISK == 1) |
        (CHALLENGING_DAYS_RISK == 1) |
        (MANAGE_STRESS_RISK == 1) |
        (STRESS_INCREASED == 1) |
        (COPING_DECREASED == 1) |
        (DAYS_CHALLENGING_INCREASED == 1) |
        (DEP_ANX_INCREASED == 1)
    ),
    ANY_RISK = as.integer(
      any(BAD_DAY_RISK == 1,
          STRESS_RISK == 1,
          DEP_ANX_RISK == 1,
          CHALLENGING_DAYS_RISK == 1,
          MANAGE_STRESS_RISK == 1,
          STRESS_INCREASED == 1,
          COPING_DECREASED == 1,
          DAYS_CHALLENGING_INCREASED == 1,
          DEP_ANX_INCREASED == 1,
          na.rm = TRUE))
  ) %>%
  ungroup() %>%
  arrange(USERID, EVENTDATE)

### How to define moderate/elevated/high-risk for those who indicate a drop in ability to cope (COPING_DECREASED)

Comp_DF$ANY_RISK <- ifelse(is.na(Comp_DF$ANY_RISK), 0, Comp_DF$ANY_RISK)

Comp_DF$PERIOD_RISK <- ifelse(is.na(Comp_DF$PERIOD_RISK), 0, Comp_DF$PERIOD_RISK)

second_cols <- names(Comp_DF)[3:30] 

### Event Totals Between Monthly Assessment Types

for (col in second_cols) {
  sum_col <- paste0(col, "_MONTHLY_SUM")
  
  Comp_DF <- Comp_DF %>%
    group_by(USERID) %>%
    arrange(USERID, EVENTDATE) %>%
    mutate(period = cumsum(!is.na(MONTHLY))) %>%
    group_by(USERID, period) %>%
    mutate(!!sum_col := sum(.data[[col]], na.rm = TRUE)) %>%
    ungroup() %>%
    select(-period)
}

### Event Totals Between Daily Check-in Assessment Types

for (col in second_cols) {
  sum_col <- paste0(col, "_DAILY_SUM")
  
  Comp_DF <- Comp_DF %>%
    group_by(USERID) %>%
    arrange(USERID, EVENTDATE) %>%
    mutate(period = cumsum(!is.na(DAILY))) %>%
    group_by(USERID, period) %>%
    mutate(!!sum_col := sum(.data[[col]], na.rm = TRUE)) %>%
    ungroup() %>%
    select(-period)
}

Comp_DF <- Comp_DF %>%
  mutate(across(
      ends_with("_SUM"),
    ~ lag(.x)
  ))

```

## Subsetting to Monthly and Daily Trend Analysis File

``` {r Subsetting_analytic_files}

Monthly_DF <- Comp_DF[which(Comp_DF$MONTHLY == 1), -c(3:30)]  ### Update columns here if needed to remove appropriate vars

Monthly_DF$TOTAL_JOURNEY_USE_M <- rowSums(Monthly_DF[grep("MONTHLY_SUM", names(Monthly_DF))])

Monthly_DF_Risk <- Monthly_DF[which(Monthly_DF$ANY_RISK == 1),]

Monthly_DF_Risk_R <- Monthly_DF_Risk[, -grep("_SUM", names(Monthly_DF_Risk))]

obs_per_person <- table(Monthly_DF_Risk_R$USERID)

Monthly_DF_Risk_Modeling <- Monthly_DF_Risk_R[Monthly_DF_Risk_R$USERID %in% names(obs_per_person[obs_per_person >= 3]), ]

Daily_DF <- Comp_DF[which(Comp_DF$DAILY == 1), -c(3:30)]  ### Update columns here if needed to remove appropriate vars

Daily_DF$TOTAL_JOURNEY_USE_D <- rowSums(Daily_DF[grep("DAILY_SUM", names(Daily_DF))])

Daily_DF_Risk <- Daily_DF[which(Daily_DF$ANY_RISK == 1),]

Daily_DF_Risk_R <- Daily_DF_Risk[, -grep("_SUM", names(Daily_DF_Risk))]

obs_per_person <- table(Daily_DF_Risk_R$USERID)

Daily_DF_Risk_Modeling <- Daily_DF_Risk_R[Daily_DF_Risk_R$USERID %in% names(obs_per_person[obs_per_person >= 3]), ]

Monthly_Dep_Anx_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 1),]

Monthly_Dep_Anx_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 2),]

Monthly_Dep_Anx_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 3),]

Monthly_Stress_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 1),]

Monthly_Stress_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 2),]

Monthly_Stress_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 3),]

```

``` {r sample_size_frequencies}


### Based on the information Journey has provided, there appear to be approximately 6,700 participants with repeated assessment ### data and roughly 10,600 participants with repeated daily check-ins.
d

Comp_DF %>%
  count(USERID) %>%
  #filter(n > 2) %>%
  summarise(distinct_users = n())

Daily_Checks %>%
  group_by(USERID) %>%
  summarise(
    sum_daily   = sum(DAILY, na.rm = TRUE)
  ) %>%
  filter(sum_daily > 1) %>%
  summarise(distinct_users = n())


Monthly_Assessments %>%
  group_by(USERID) %>%
  summarise(
    sum_monthly = sum(MONTHLY, na.rm = TRUE)
  ) %>%
  filter(sum_monthly > 1) %>%
  summarise(distinct_users = n())


  Comp_DF %>%
  group_by(USERID) %>%
  summarise(
    sum_daily   = sum(DAILY, na.rm = TRUE),
    sum_monthly = sum(MONTHLY, na.rm = TRUE)
  ) %>%
  filter(sum_daily > 1 & sum_monthly > 1) %>%
  summarise(distinct_users = n())


```

``` {r monthly_out_pred_correlations}

Outcomes <- c("STRESSLEVEL", "MANAGEFEELINGSLEVEL", "FEELINGSFREQUENCY", "DAYSEMOTIONALLYCHALLENGING", "MANAGESTRESSLEVEL")

Pred_Out_M <- Monthly_DF[, which(grepl("MONTHLY_SUM", names(Monthly_DF)) | names(Monthly_DF) %in% Outcomes)]

Cors_list <- NULL

for (i in Outcomes) {

ctest_M <- corr.test(Pred_Out_M)
r_value_M <- round(ctest_M$r[, i], 4)
p_value_M <- round(ctest_M$p[, i], 4)
n_value_M <- ctest_M$n[, i]

Monthly_Cors <- data.frame(Correlation = r_value_M, P_Value = p_value_M, N = n_value_M, Outcome = i)

Monthly_Cors$Predictor <- sub(".*\\.", "", rownames(Monthly_Cors))

  Cors_list[[i]] <- Monthly_Cors
  
}

Monthly_Cors_DF <- do.call(rbind, Cors_list)

rownames(Monthly_Cors_DF) <- NULL

```

``` {r daily_out_pred_correlations}

Pred_Out_D <- Daily_DF[, which(grepl("DAILY_SUM", names(Monthly_DF)) | names(Monthly_DF) %in% Outcomes)]

for (i in Outcomes){

ctest_D <- corr.test(Pred_Out_D)
r_value_D <- round(ctest_D$r[, i], 4)
p_value_D <- round(ctest_D$p[, i], 4)
n_value_D <- ctest_D$n[, i]

Daily_Cors <- data.frame(Correlation = r_value_D, P_Value = p_value_D, N = n_value_D, Outcome = i)

Daily_Cors$Predictor <- sub(".*\\.", "", rownames(Daily_Cors))

  Cors_list[[i]] <- Daily_Cors
  
}

Daily_Cors_DF <- do.call(rbind, Cors_list)

rownames(Daily_Cors_DF) <- NULL

```

``` {r monthly_analyses}

###Risk Signals → Journey Use → Improvement
###Risk Signals → Journey Use → No Improvement
###Risk Signals → Limited/No Journey Use → Worsening Risk

# Standardize (z-score) TOTAL_JOURNEY_USE_M

Monthly_DF_Risk_Modeling <- Monthly_DF_Risk_Modeling %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_DF_Risk_Modeling$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_DF_Risk_Modeling$TOTAL_JOURNEY_USE_M)[,1]





















# Random intercept model: allows each person to have their own baseline stress level

model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_M_z | USERID), data = Monthly_DF_Risk_Modeling)

summary(model1)

```

``` {r daily_analyses}

###Risk Signals → Journey Use → Improvement
###Risk Signals → Journey Use → No Improvement
###Risk Signals → Limited/No Journey Use → Worsening Risk



# Install and load the tvem and tidyverse packages

# Example formula where the effect of 'predictor1' varies over 'time'
# grouped by 'subject_id'
tvem_model_D <- tvem(
  formula = FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z,
  data = Daily_DF_Risk_Modeling,
  id = USERID,
  time = DATE_NUMERIC,
  family = gaussian() # Use binomial() for binary outcomes
)

# View the summary of the varying coefficients
summary(tvem_model_D)

# Adjust index/name based on what str() shows you
coef_df_D <- tvem_model_D$grid_fitted_coefficients$TOTAL_JOURNEY_USE_D_z

coef_df_D$time <- tvem_model_D$time_grid

library(ggplot2)

ggplot(coef_df_D, aes(x = time)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "steelblue", alpha = 0.2) +
  geom_line(aes(y = estimate), color = "steelblue", linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Time-Varying Effect of Total Use on Stress Level",
    x = "Time (days since first observation)",
    y = "Estimated Effect of Total Daily Journey Use on STRESSLEVEL"
  ) +
  theme_minimal(base_size = 13)












# Standardize (z-score) TOTAL_JOURNEY_USE_M

Daily_DF_Risk_Modeling$TOTAL_JOURNEY_USE_D_z <- scale(Daily_DF_Risk_Modeling$TOTAL_JOURNEY_USE_D)[,1]

Daily_DF_Risk_Modeling <- Daily_DF_Risk_Modeling %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z + (1 | USERID), data = Daily_DF_Risk_Modeling)

summary(model1)

model2 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z + (1 + TOTAL_JOURNEY_USE_D_z | USERID), data = Daily_DF_Risk_Modeling)

summary(model2)

model3 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z * DATE_NUMERIC + (1 | USERID), data = Daily_DF_Risk_Modeling)

summary(model3)

model4 <- lmer(FEELINGRATING ~ TOTAL_JOURNEY_USE_D_z * DATE_NUMERIC + (1 + TOTAL_JOURNEY_USE_D_z | USERID), data = Daily_DF_Risk_Modeling)

summary(model4)

```





``` {r daily_model_plots}

predictions <- ggpredict(model3, terms = "TOTAL_JOURNEY_USE_D_z")

# 3. Plot automatically using ggplot2 logic under the hood
plot(predictions)

# Alternatively, customize it further with standard ggplot2 layers
ggplot(predictions, aes(x = x, y = predicted)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "blue") +
  labs(x = "Days", y = "Predicted Reaction Time", title = "Model Fixed Effects")









```


``` {r tvem_monthly_test}

tvem_model_M <- tvem(
  formula = STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z,
  data = Monthly_Dep_Anx_GRP_1,
  id = USERID,
  time = DATE_NUMERIC,
  family = gaussian() # Use binomial() for binary outcomes
)

# Adjust index/name based on what str() shows you
coef_df_M <- tvem_model_M$grid_fitted_coefficients$TOTAL_JOURNEY_USE_M_z

coef_df_M$time <- tvem_model_M$time_grid

ggplot(coef_df_M, aes(x = time)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "steelblue", alpha = 0.2) +
  geom_line(aes(y = estimate), color = "steelblue", linewidth = 1) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Time-Varying Effect of Total Use on Stress Level",
    x = "Time (days since first observation)",
    y = "Estimated Effect of Total Daily Journey Use on STRESSLEVEL"
  ) +
  theme_minimal(base_size = 13)




```


























``` {r monthly_analyses}

###Risk Signals → Journey Use → Improvement
###Risk Signals → Journey Use → No Improvement
###Risk Signals → Limited/No Journey Use → Worsening Risk

# Standardize (z-score) TOTAL_JOURNEY_USE_M


Monthly_Dep_Anx_GRP_1 <- Monthly_Dep_Anx_GRP_1 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_1$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_1$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_1)

summary(model1)






Monthly_Dep_Anx_GRP_2 <- Monthly_Dep_Anx_GRP_2 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_2$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_2$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_2)

summary(model1)












Monthly_Dep_Anx_GRP_3 <- Monthly_Dep_Anx_GRP_3 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)
















Monthly_Stress_GRP_1 <- Monthly_Stress_GRP_1 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Stress_GRP_1$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Stress_GRP_1$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_1)

summary(model1)






Monthly_Stress_GRP_2 <- Monthly_Stress_GRP_2 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Stress_GRP_2$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Stress_GRP_2$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_2)

summary(model1)












Monthly_Stress_GRP_3 <- Monthly_Stress_GRP_3 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Stress_GRP_3$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Stress_GRP_3$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGESTRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(MANAGEFEELINGSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(FEELINGSFREQUENCY ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(DAYSEMOTIONALLYCHALLENGING ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Stress_GRP_3)

summary(model1)

```

Monthly_Dep_Anx_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 1),]

Monthly_Dep_Anx_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 2),]

Monthly_Dep_Anx_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$DEP_ANX_RISK_GROUP == 3),]

Monthly_Stress_GRP_1 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 1),]

Monthly_Stress_GRP_2 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 2),]

Monthly_Stress_GRP_3 <- Monthly_DF_Risk_Modeling[which(Monthly_DF_Risk_Modeling$STRESS_RISK_GROUP == 3),]






Monthly_Dep_Anx_GRP_3 <- Monthly_Dep_Anx_GRP_3 %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_Dep_Anx_GRP_3$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + (1 | USERID), data = Monthly_Dep_Anx_GRP_3)

summary(model1)

```{r sandbox}

table(Daily_DF$ANY_RISK)

table(Monthly_DF$ANY_RISK)

Monthly_DF$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_DF$TOTAL_JOURNEY_USE_M)[,1]


Monthly_DF <- Monthly_DF %>%
  group_by(USERID) %>%
  mutate(DATE_NUMERIC = as.numeric(EVENTDATE - min(EVENTDATE)) + 1) %>%
  ungroup()

Monthly_DF$TOTAL_JOURNEY_USE_M_z <- scale(Monthly_DF$TOTAL_JOURNEY_USE_M)[,1]

# Random intercept model: allows each person to have their own baseline stress level
model1 <- lmer(STRESSLEVEL ~ TOTAL_JOURNEY_USE_M_z * DATE_NUMERIC + ANY_RISK + (1 | USERID), data = Monthly_DF)

summary(model1)


testdf <- testdf[, -c(27:82)]

model1 <- lmer(TOTAL_JOURNEY_USE_M_z ~ ANY_RISK + (1 | USERID), data = testdf)

summary(model1)


testdf <- Comp_DF#[which(!is.na(Comp_DF$STRESS_INCREASED)),]

testdf <- testdf[, -c(3:30,56:111)]

transitioned_users <- testdf %>%
  arrange(USERID, EVENTDATE) %>%
  group_by(USERID) %>%
  mutate(ever_zero_so_far = cummax(PERIOD_RISK == 0)) %>%
  filter(PERIOD_RISK == 1 & lag(ever_zero_so_far, default = FALSE)) %>%
  ungroup() %>%
  distinct(USERID) %>%
  pull(USERID)

# Step 2: Subset to keep ALL rows for those USERIDs
transitioned_data <- testdf %>%
  filter(USERID %in% transitioned_users)

# Quick checks
length(transitioned_users)               # number of people who transitioned
length(unique(transitioned_data$USERID)) # should match the above
table(transitioned_data$ANY_RISK)        # should include both 0s and 1s

sum(is.na(transitioned_data$ANY_RISK))











```
